### 2013-11-29 paper/main.tex
eliminated use of Bloques for TikZ directly
All uses of Bloques, a library for creating control system
diagrams, has been removed.  It did produce some nice graphics
but it was inflexible and difficult to fine tune.
Creating control system diagrams directly in TikZ along with
styles produces better results and is easier to maintain.

%\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{nonfloat}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{bloques}
\usepackage{fullpage}

\usepackage{tikz}
\usetikzlibrary{calc,arrows,positioning}
% control system tikz objects
\tikzset{shadow/.style={drop shadow={opacity=0.8},fill=white}}
\tikzset{sum/.style={circle,draw,very thick,shadow,minimum size=6mm}}
\tikzset{sumnp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{below left,xshift=1.0mm,yshift=1.0mm}:$-$}} }
\tikzset{sumxpxp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{above right,xshift=-1.0mm,yshift=-1.0mm}:$+$}} }
\tikzset{gain/.style={rectangle,draw,very thick,inner sep=2mm,shadow}}

@@

\section{Model}

@@

\xdistance{1.8cm}
\ydistance{2.0cm}

\begin{figure}[hbp!]
\begin{center}
\begin{tikzpicture}
\bShadow
\bStart{$\Delta \text{control}$}
\bGain{$1.699$}
\bMinusF{S1}
\bGain{$\dfrac{8.5683}{z^2 - 0.9025 z}$}
\bMinusUp{$\Delta \text{torque}$}
\bGain{$\dfrac{2.98}{z - 0.9354}$}
\bGainFeedBack{$0.000093$}{S1}
\bEnd{$\Delta \text{rpm}$}
\end{tikzpicture}
\end{center}
\caption{Linear engine model.}\label{fig:lem}
\end{figure}

>>>>

%\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{nonfloat}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{fullpage}

\usepackage{tikz}
\usetikzlibrary{calc,arrows,positioning,shadows}
% control system tikz objects
\tikzset{shadow/.style={drop shadow,fill=white}}
\tikzset{sum/.style={circle,draw,very thick,shadow,minimum size=6mm}}
\tikzset{sumnp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{below left,xshift=1.0mm,yshift=1.0mm}:$-$}} }
\tikzset{sumpn/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{above right,xshift=-1.0mm,yshift=-1.0mm}:$-$}} }
\tikzset{sumxpxp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{above right,xshift=-1.0mm,yshift=-1.0mm}:$+$}} }
\tikzset{gain/.style={rectangle,draw,very thick,inner sep=2mm,shadow}}

@@

\section{Engine Model}

@@

\begin{figure}[hbp!]
\begin{center}

\begin{tikzpicture}[>=triangle 60, scale=0.8,
	node distance=14mm, auto]

	\node[gain] 	(gain1)	[]					{$1.699$};
	\node[sumnp]  	(sum1)	[right=of gain1] 	{};
	\node[gain] 	(gain2)	[right=of sum1]		{$\dfrac{8.5683}{z^2-0.9025z}$};
	\node[sumpn]  	(sum2)	[right=of gain2] 	{};
	\node[gain] 	(gain3)	[right=of sum2]		{$\dfrac{2.98}{z - 0.9534}$};
	\node[gain] 	(gain4)	[below=of sum2]		{$0.000093$};

	\draw [->] (-20mm,0) node[above]{$\Delta \text{control}$} -- (gain1.west);
	\draw [->] (gain1) -- (sum1);
	\draw [->] (sum1) -- (gain2);
	\draw [->] (gain2) -- (sum2);
	\draw [->] (sum2) -- (gain3);
	\draw [->] (gain3.east) -- ++(20mm,0) node[above]{$\Delta \text{rpm}$};
	\draw [->] ($(gain3.east) + (10mm,0) $) |- (gain4.east);
	\draw [->] (gain4.west) -| (sum1.south);
	\draw [<-] (sum2.north) -- ++(0,10mm) node[above]{$\Delta \text{torque}$};
\end{tikzpicture}

\end{center}
\caption{Linear engine model.}\label{fig:lem}
\end{figure}
